Learning Distributed Word Representations for Natural Logic Reasoning

### 2015-01-08 writing/AAAI SSS '15/BowmanPottsManning.tex
A couple of new refs

Natural logic offers a powerful \emph{relational} conception of
semantics: the meanings for expressions are given, at least in part,
by their inferential connections with other expressions
\cite{vanBenthem08NATLOG,maccartney2009extended}. For instance,
\word{turtle} is analyzed, not primarily by its extension in the
world, but rather by its lexical network: it entails \word{reptile},
excludes \word{chair}, is entailed by \word{sea
  turtle}, and so forth. With generalized notions of entailment and
contradiction, these relationships can be defined for all lexical
categories as well as complex phrases, sentences, and even texts. The
resulting theories of meaning offer valuable new analytic tools for
tasks involving database inference, relation extraction, and textual
entailment.

@@

	\end{picture}
	%}
        \caption{The model structure used to compare \ii{turtle} and
          \ii{animal}.  learned word representations are fed through
          either an NN or NTN comparison network and then to a softmax
        classifier over the seven relations in Table~\ref{b-table}.}
  \label{sample-figure}
\end{figure}

@@

Using simulated data as above is reassuring about what the models
learn and why, but we also want to know how they perform with a real
natural language vocabulary. Unfortunately, as far as we are aware,
there are no available resources labeling such a vocabulary with the
relations from Table~\ref{b-table}. However, the relations in WordNet
\cite{fellbaum2010wordnet} come close and pose the same substantive
challenges within a somewhat easier classification problem.

@@

This investigation builds upon extensive prior research on
constructing compositional word meanings in vector spaces
\cite{ClarkCoeckeSadrzadeh2011,grefenstette2013towards,Hermann-etal:2013,rocktaschellow},
extracting entailment information from distributional vector space
models \cite{baroni2012entailment,rei2014looking}, and transferring
information between logic programs and neural networks in constrained
settings \cite{holldobler1999approximating,hitzler2004logic}. Our
primary contribution is to establish a tight connection between these
approaches and formal developments within natural logic.  More
specifically, we showed that neural network models, optimized using
established techniques, can learn distributed representations that
closely approximate the behavior one would expect from a natural logic
inference algorithm.

>>>>

Natural logic offers a powerful \emph{relational} conception of
semantics: the meanings for expressions are given, at least in part,
by their inferential connections with other expressions
\cite{Katz72,maccartney2009extended,vanBenthem08NATLOG}. For instance,
\word{turtle} is analyzed, not primarily by its extension in the
world, but rather by its lexical network: it entails \word{reptile},
excludes \word{chair}, is entailed by \word{sea
  turtle}, and so forth. With generalized notions of entailment and
contradiction, these relationships can be defined for all lexical
categories as well as complex phrases, sentences, and even texts. The
resulting theories of meaning offer valuable new analytic tools for
tasks involving database inference, relation extraction, and textual
entailment.

@@

	\end{picture}
	%}
        \caption{The model structure used to compare \ii{turtle} and
          \ii{animal}.  Learned word representations are fed through
          either an NN or NTN comparison layer and then to a softmax
        classifier over the seven relations in Table~\ref{b-table}.}
  \label{sample-figure}
\end{figure}

@@

Using simulated data as above is reassuring about what the models
learn and why, but we also want to know how they perform with a real
natural language vocabulary. Unfortunately, as far as we are aware,
there are no available resources labeling such a vocabulary with the
relations from Table~\ref{b-table}. However, the relations in WordNet
\cite{fellbaum2010wordnet,WordNet95} come close and pose the same substantive
challenges within a somewhat easier classification problem.

@@

This investigation builds upon extensive prior research on
constructing compositional word meanings in vector spaces
\cite{ClarkCoeckeSadrzadeh2011,grefenstette2013towards,Hermann-etal:2013,rocktaschellow},
extracting entailment information from distributional vector space
models \cite{baroni2012entailment,rei2014looking}, and transferring
information between logic programs and neural networks in constrained
settings \cite{hitzler2004logic,holldobler1999approximating}. Our
primary contribution is to establish a tight connection between these
approaches and formal developments within natural logic.  More
specifically, we showed that neural network models, optimized using
established techniques, can learn distributed representations that
closely approximate the behavior one would expect from a natural logic
inference algorithm.
